---
title: "User acceptance testing with ExpectUserAccepts"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{User acceptance testing with ExpectUserAccepts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Some quality requirements can't be verified by automated tests. Aesthetic changes to an HTML report, layout adjustments, or visual design updates require a human to look at the result and confirm it meets expectations. `ExpectUserAccepts()` bridges this gap by connecting `{testthat}` tests to GitHub issues that a reviewer can close to indicate acceptance.

This extends the test coverage that `{qcthat}` tracks to include things that only a person can verify — which is often exactly what matters most to stakeholders.

The workflow involves three roles:

- 🧑‍💻 **PD** (Program Developer): writes the code fix and the acceptance test
- 💼 **USR** (User/Reviewer): inspects the result and closes the issue to accept
- 🤖 **AUTO** (Automated System): re-runs the test suite when the issue is closed

## The scenario

Suppose issue `#42` documents an aesthetic problem: the HTML report header uses outdated brand colors. A developer creates branch `fix-42`, implements the CSS changes, and needs sign-off from a non-technical reviewer before the fix is considered complete.

The developer adds a test:

```{r, eval=FALSE}
test_that("report header uses the updated brand colors (#42)", {
  ExpectUserAccepts(
    strDescription = "Report header uses updated brand colors",
    intIssue = 42L,
    chrInstructions = "Open the report at https://example.com/preview and inspect the header.",
    chrChecks = c(
      "Header background is #59488f",
      "Logo is centered and not clipped",
      "Font renders as Montserrat on the title"
    ),
    chrAssignees = "design-reviewer"
  )
})
```

- `strDescription` — a short summary that becomes the sub-issue title.
- `intIssue` — the parent GitHub issue number (`#42`).
- `chrInstructions` — optional context for the reviewer, such as a link to a preview deployment.
- `chrChecks` — checkbox items the reviewer will see in the sub-issue body.
- `chrAssignees` — GitHub username(s) of the reviewer(s) to assign.

## What happens behind the scenes

When the test runs, `ExpectUserAccepts()` performs the following steps:

1. **Guard checks.** The function only executes when not on CRAN, inside a git repository, and online. Otherwise it silently returns without side effects.

2. **Issue lookup.** Searches for an existing child issue of `#42` with the `qcthat-uat` label and a matching title (`"qcthat Acceptance for #42: Report header uses updated brand colors"`).

3. **Issue creation.** If no matching child issue exists, creates one as a sub-issue of `#42` with:
   - The title above
   - A body containing: *"Close this issue to indicate your acceptance."*, the `chrInstructions` text, and checkbox items from `chrChecks`
   - The `qcthat-uat` label

4. **Assignment.** Assigns the specified GitHub user(s). If the issue was previously closed and a new assignee is added, it is automatically re-opened.

5. **State check.**
   - If the sub-issue is **closed**: `testthat::pass()`.
   - If the sub-issue is **open**: `testthat::fail()`, but only when `lglReportFailure` is `TRUE`. By default this is controlled by the `qcthat_UAT` environment variable (see [Environment variables]).

6. **Logging.** Records the result to an internal registry used by `CommentUAT()` to post status reports on pull requests.

During local development, the test **does not fail** by default because the `qcthat_UAT` environment variable is not set. It only reports failures in the GitHub Actions workflow where `qcthat_UAT: true` is configured.

## The reviewer's workflow

1. 💼 The reviewer receives a GitHub notification for the assigned sub-issue.
2. The issue body lists the checks as checkboxes and includes any instructions.
3. The reviewer inspects the report (e.g., on a deployed preview or locally) and works through the checklist.
4. If satisfied, the reviewer **closes the issue** to indicate acceptance.
5. If changes are needed, the reviewer **comments** with required changes and leaves the issue open.

## GitHub Actions integration

The `qcthat.yaml` workflow (installed via `use_qcthat()`) handles the automated side:

1. When a `qcthat-uat` labeled issue is **closed**, the workflow fires on the `issues: [closed]` event.
2. The workflow runs `TriggerUAT()`, which finds open pull requests referencing the closed issue.
3. If no workflow run is already in progress for those PRs, the QC workflow is re-triggered.
4. On re-run, the test suite executes again. This time `ExpectUserAccepts()` sees the sub-issue is closed and calls `testthat::pass()`.
5. The UAT report comment on the PR is updated to reflect the accepted state.

This means the reviewer does not need to understand R, `{testthat}`, or the CI system. They just close a GitHub issue.

## Environment variables

| Variable | Purpose | Default |
|---|---|---|
| `qcthat_UAT` | Set to `"TRUE"` to make open UAT issues report as test failures. Checked by `IsCheckingUAT()`. | `""` (failures are not reported) |
| `qcthat_UAT_ASSIGNEES` | Comma-separated GitHub usernames for default assignees. | `""` |

Both are typically set in `.github/workflows/qcthat.yaml` rather than locally.

## Tips

- Keep `strDescription` short and specific — it becomes the sub-issue title.
- Use `chrInstructions` to link the reviewer to a preview deployment or specific page in the report.
- Multiple `ExpectUserAccepts()` calls can exist in the same test file, each tracking a different aspect of the same issue or different issues.
- You can set assignees via the `qcthat_UAT_ASSIGNEES` environment variable in your workflow YAML instead of hard-coding usernames. This allows different assignees per branch target:

```{r, eval=FALSE}
# In your workflow YAML:
# qcthat_UAT_ASSIGNEES: "design-reviewer,product-owner"

# In your test — uses the env var by default:
test_that("dashboard layout matches mockup (#55)", {
  ExpectUserAccepts(
    strDescription = "Dashboard layout matches mockup",
    intIssue = 55L,
    chrChecks = c(
      "Sidebar collapses on mobile",
      "Charts are responsive"
    )
  )
})
```
