---
title: "Setup"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Setup}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

To utilize `{qcthat}`, you must 

1. Use GitHub Issues to document package requirements (see [Chapter 20: Software development practices from *R Packages (2e)* by Hadley Wickham and Jennifer Bryan](https://r-pkgs.org/software-development-practices.html) and `usethis::use_github()`).
2. Use `{testthat}` to verify the implementation of those requirements (see the [Testing section of *R Packages (2e)* by Hadley Wickham and Jennifer Bryan](https://r-pkgs.org/testing-basics.html) and `usethis::use_testthat()`).
3. Link tests to issues by including `(#{issue_number})` in the test description, such as:

```{r, eval=FALSE}
test_that("Users can view a matrix of GitHub issues and test results (#31)", {
  # Expectations that prove that this worked.
})
```

## Activating {qcthat}

```{r use_qcthat, eval=FALSE}
qcthat::use_qcthat()
```

Run `use_qcthat()` from within your package directory to:

1. Create GitHub labels (`SetupGHLabels()`) with the default labels that `{qcthat}` uses to assist in reporting: `r qcthat::DefaultIgnoreLabels()`.
2. Install a GitHub Action (`Action_qcthat()`) that will automatically generate QC reports and user acceptance reports on pull requests and releases. You can customize the behavior of this action by modifying the YAML file in `.github/workflows/qcthat.yaml`.

## Bootstrapping test tags with AI

```{r Skill_TagTestsWithIssues, eval=FALSE}
qcthat::Skill_TagTestsWithIssues()
```

Run `Skill_TagTestsWithIssues()` to install an experimental `SKILL.md` file to help you use AI to tag your tests with GitHub issue numbers. Tell your agent to use the skill with "tag tests" with issues" (or by pointing to the installed skill file, depending on your setup). Read more about AI agent skills at [agentskills.io](https://agentskills.io/home). Note: This might use a *lot* of tokens, depending on the number of tests and issues that you have in your repository.

As part of the tagging process, your agent will generate a log of its reasoning in `pkgdown/assets/test_tag_reasons.qmd`, rendered to html as `pkgdown/assets/test_tag_reasons.html`. If you use pkgdown, you can view this file at "test_tag_reasons.html" (relative to your site, locally or deployed).

**Review all tags generated by the agent carefully.**

After you produce this initial set of tags, we recommend deleting the `SKILL.md` file and the `test_tag_reasons` files. They are only intended to get you started.
